---
title: "GHYP"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: https://github.com/Reckziegel/SimGHYP
    social:
    - facebook
    - twitter
    - google-plus
    - linkedin
    theme:
      bootswatch: sandstone
      version: 4
      bg: '#fff'
      fg: '#063852'
      navbar-bg: '#063852'
      base_font:
        google: Play
runtime: shiny
resource_files:
- images/GHYP_dashboard-03.png
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tibble)
library(ghyp)
library(plotly)
#source("functions/plot_ghyp_triangle.R")
#source("functions/xichi.R")
```

# Sidebar {.sidebar}

```{r}
shiny::selectInput(
  inputId = "input_dist_type", 
  label   = h4("Distribution"), 
  choices = list(
    "Normal"                 , 
    "Student-t"              ,
    "Variance-Gamma"         ,
    "Normal-Inverse Gaussian",
    "Hyperbolic"             ,
    "Generalized Hyperbolic" 
    ), 
  selected = 1
)

h4("Simulation Inputs")

shiny::sliderInput(
  inputId = "input_n", 
  label   = "Number of Draws", 
  min = 100, 
  max = 2000, 
  step = 100, 
  value = 100
)

shiny::sliderInput(
  inputId = "input_mu", 
  label   = "Mean", 
  min = -5, 
  max = 5, 
  step = 0.25, 
  value = 0
)

shiny::sliderInput(
  inputId = "input_sigma", 
  label   = "Sigma", 
  min = 0.01, 
  max = 5, 
  step = 0.25, 
  value = 2.5
)

# Student-t Params
shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Student-t'", 
  shiny::sliderInput(
    inputId = "input_nu", 
    label   = "Nu (Degrees os Freedom)", 
    min     = 3, 
    max     = 50, 
    step    = 1, 
    value   = 5
  )
)

# NIG Params
shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Normal-Inverse Gaussian'", 
  shiny::sliderInput(
    inputId = "input_gamma_nig", 
    label   = "Gamma (Assimetry)", 
    min     = -5, 
    max     = 5, 
    step    = 0.25, 
    value   = 0
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Normal-Inverse Gaussian'", 
  shiny::sliderInput(
    inputId = "input_psi_nig", 
    label   = "Psi", 
    min     = 0.01, 
    max     = 10, 
    step    = 0.25, 
    value   = 2
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Normal-Inverse Gaussian'", 
  shiny::sliderInput(
    inputId = "input_chi_nig", 
    label   = "Chi", 
    min     = 0.01, 
    max     = 10, 
    step    = 0.25, 
    value   = 2
  )
)

# VG Params
shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Variance-Gamma'",
  shiny::sliderInput(
    inputId = "input_gamma_vg",
    label   = "Gamma (Assimetry)",
    min     = -10,
    max     = 10,
    step    = 1,
    value   = 0
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Variance-Gamma'",
  shiny::sliderInput(
    inputId = "input_psi_vg",
    label   = "Psi",
    min     = 1,
    max     = 10,
    step    = 1,
    value   = 2
  )
)

# HYP Params
shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_gamma_hyp", 
    label   = "Gamma (Assimetry)", 
    min     = -5, 
    max     = 5, 
    step    = 0.25, 
    value   = 0
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_psi_hyp", 
    label   = "Psi", 
    min     = 1, 
    max     = 20, 
    step    = 1, 
    value   = 2
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_chi_hyp", 
    label   = "Chi", 
    min     = 0.5, 
    max     = 20, 
    step    = 1, 
    value   = 0.5
  )
)

# GHY Params
shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Generalized Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_gamma_ghyp", 
    label   = "Gamma (Assimetry)", 
    min     = -5, 
    max     = 5, 
    step    = 0.25, 
    value   = 0
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Generalized Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_psi_ghyp", 
    label   = "Psi", 
    min     = 1, 
    max     = 20, 
    step    = 1, 
    value   = 2
  )
)

shiny::conditionalPanel(
  condition = "input.input_dist_type == 'Generalized Hyperbolic'", 
  shiny::sliderInput(
    inputId = "input_chi_ghyp", 
    label   = "Chi", 
    min     = 0.5, 
    max     = 20, 
    step    = 1, 
    value   = 0.5
  )
)
```

```{r}
seq_ <- reactive({
  seq(-15, 15, length.out = input$input_n)
})
```

# The Distribution {data-icon="fa-infinity"}

## Column {data-width="500"}

```{r}
# objects used latter for plotting

# Distribution Specification
dist_object_ <- reactive({
  if (input$input_dist_type == 'Normal') {
    gauss(mu = input$input_mu, sigma = input$input_sigma)
  } else if (input$input_dist_type == 'Student-t') {
    student.t(nu = input$input_nu, mu = input$input_mu, sigma = input$input_sigma)
  } else if (input$input_dist_type == 'Variance-Gamma') {
    VG(mu = input$input_mu, sigma = input$input_sigma, gamma = input$input_gamma_vg, 
       psi = input$input_psi_vg)
  } else if (input$input_dist_type == 'Normal-Inverse Gaussian') {
    NIG(mu = input$input_mu, sigma = input$input_sigma, gamma = input$input_gamma_nig, 
        chi = input$input_chi_nig, psi = input$input_psi_nig)
  } else if (input$input_dist_type == "Hyperbolic") {
    hyp(mu = input$input_mu, chi = input$input_chi_hyp, psi = input$input_psi_hyp,
        sigma = input$input_sigma, gamma = input$input_gamma_hyp)
  } else {
    ghyp(chi = input$input_chi_ghyp, psi = input$input_psi_ghyp, mu = input$input_mu, 
         sigma = input$input_sigma, gamma = input$input_gamma_ghyp)
  }
}) 

# Random Number Generation
random_ghyp_ <- reactive({
  rghyp(n = length(seq_()), object = dist_object_())
})

# Distribution Estimation
dist_fit_ <- reactive({
  if (input$input_dist_type == 'Normal') {
    fit.gaussuv(random_ghyp_())
  } else if (input$input_dist_type == 'Student-t') {
    fit.tuv(random_ghyp_(), silent = TRUE)
  } else if (input$input_dist_type == 'Variance-Gamma') {
    fit.VGuv(random_ghyp_(), silent = TRUE)
  } else if (input$input_dist_type == 'Normal-Inverse Gaussian') {
    fit.NIGuv(random_ghyp_(), silent = TRUE)
  } else if (input$input_dist_type == "Hyperbolic") {
    fit.hypuv(random_ghyp_(), silent = TRUE)
  } else { 
    fit.ghypuv(random_ghyp_(), silent = TRUE)
  }
})
```

### Probability Density Function (PDF)

```{r}
plot_pdf_ <- reactive({
  tibble(
    x = seq_(),
    y = dghyp(x = seq_(), object = dist_object_())
  )
})

renderPlotly({
  plot_ly(data = plot_pdf_(), x = ~x, y = ~y, type = "scatter", mode = "lines", 
          color = I("#063852")) |> 
    layout(xaxis = list(title = "x"), yaxis = list(title = "Probability"))
})
```

### Cumulative Density Function (CDF)

```{r}
plot_cdf_ <- reactive({
  tibble(
    x = seq_(),
    y = pghyp(q = seq_(), object = dist_object_())
  )
})

renderPlotly({
  plot_ly(data = plot_cdf_(), x = ~x, y = ~y, type = "scatter", mode = "lines",
          color = I("#063852")) |> 
    layout(xaxis = list(title = "x"), yaxis = list(title = "Probability"))
})
```

## Column {data-width="500"}

### Quantile Distribution

```{r}
plot_quantile_ <- reactive({
  tibble(
    x = seq_(),
    y = qghyp(p      = seq(0.001, 0.999, length.out = length(seq_())),
              object = dist_object_())
  ) 
})

renderPlotly({
  plot_ly(data = plot_quantile_(), x = ~x, y = ~y, type = "scatter", mode = 'lines', 
          color = I("#063852")) |> 
    layout(xaxis = list(title = "x"), yaxis = list(title = ""))
})
```

### Numerical Estimation

```{r}
fit_table_ <- reactive({
  
  tibble(
    Metric = c("Convergence", "Number of Iterations", "Log-Likelihood", "AIC",
               "Mu", "Sigma", "Gamma", "Alpha-bar", "Chi", "Psi"),
    Value = c(
      as.logical(dist_fit_()@converged), 
      dist_fit_()@n.iter,
      scales::number(dist_fit_()@llh, big.mark = ",", decimal.mark = "."),
      scales::number(dist_fit_()@aic, big.mark = ",", decimal.mark = "."),
      round(dist_fit_()@mu, 4),
      round(dist_fit_()@sigma, 4), 
      round(dist_fit_()@gamma, 4),
      round(dist_fit_()@alpha.bar, 4),
      round(dist_fit_()@chi, 4), 
      round(dist_fit_()@psi, 4)
    )
  )
})
renderTable(fit_table_())
```

# About {data-icon="fa-info-circle"}

```{r}
h4("Why this app?")
```

The objective of this `shiny` app is to demonstrate the flexibility of the [Generalised Hyperbolic Distribution (GHYP)](https://en.wikipedia.org/wiki/Generalised_hyperbolic_distribution){style="color: #D9B44A"}.

By construction, the Hyperbolic PDF generalizes several distributions already used in finance, making it a suitable candidate to model real world events.

This is specially true for investment strategies in which the primary focus is on capital preservation. In this case, it's crucial if the central moments of the distribution can be estimated *correctly*, otherwise tail events may be amiss.

```{r}
h4("Package Dependencies")
```

For the numerical computations in this application the [ghyp](https://cran.r-project.org/web/packages/ghyp/index.html){style="color: #D9B44A"} package is used. The graphics is constructed with [plotly](https://plotly.com/r/){style="color: #D9B44A"} and the UI relies on `shiny` and `flexdashboard` packages.

```{r}
hr()
br()
```

If you have any suggestion on how this app could be improved, please, [let me know](https://github.com/Reckziegel/SimGHYP/issues){style="color: #D9B44A"}.

You can also __share__ this application by clicking on the icons that appear on the top right. To see the full code on github go to source code. 

Best, <br> Bernardo Reckziegel <br> `r Sys.Date()` <br> **Github**: [Reckziegel](https://github.com/Reckziegel){style="color: #D9B44A"} <br> **Linkedin**: [bernardoreckziegel](https://www.linkedin.com/in/bernardoreckziegel/){style="color: #D9B44A"}
